Computing Entropies With Nested Sampling

### 2017-04-08 paper/ms.tex
More working on the precisional appendix

Consider a probability density function $f(x)$, defined on the real
line. The probability contained in an interval
$[x_0, x_0 + L]$, which has length $L$, is
\begin{align}
\int_{x_0}^{x_0 + L} f(x) \, dx &= F(x_0 + L) - F(x_0)
\end{align}
where $F(x)$ is the cumulative distribution function (CDF).
This probability can be considered as a function of two variables,
$x_0$ and $L$, which I will denote by $Q(,)$:
\begin{align}
Q(x_0, L) &= F(x_0 + L) - F(x_0).
\end{align}
The contribution of such an interval to an entropy expression
is `minus $p\log p$', i.e.
\begin{align}
h(x_0, L) &= -Q(x_0, L) \log Q(x_0, L).
\end{align}

Consider the rate of change of $h$ as the interval is shifted to
the right, but with its width $L$ held constant:
\begin{align}
\frac{\partial h}{\partial x_0} &= - \frac{\partial}{\partial x_0}
  Q(x_0, L) \log Q(x_0, L)
\end{align}

>>>>

Consider a probability density function $f(x)$, defined on the real
line. The probability contained in an interval
$[x_0, x_0 + L]$, which has length $L$, is
\begin{align}
\int_{x_0}^{x_0 + L} f(x) \, dx &= F(x_0 + L) - F(x_0)
\end{align}
where $F(x)$ is the cumulative distribution function (CDF).
This probability can be considered as a function of two variables,
$x_0$ and $L$, which I will denote by $Q(,)$:
\begin{align}
Q(x_0, L) &= F(x_0 + L) - F(x_0).
\end{align}
The contribution of such an interval to an entropy expression
is `minus $p\log p$', i.e.
\begin{align}
h(x_0, L) &= -Q(x_0, L) \log Q(x_0, L).
\end{align}
Consider the rate of change of $h$ as the interval is shifted to
the right, but with its width $L$ held constant:
\begin{align}
\frac{\partial h}{\partial x_0} &= \frac{\partial}{\partial x_0}
    \left[-Q(x_0, L) \log Q(x_0, L)\right] \\
    &= -\left[1 + \log Q(x_0, L)\right]\frac{\partial Q}{\partial x_0} \\
    &= -\left[1 + \log Q(x_0, L)\right]\left[f(x_0 + L) - f(x_0)\right].
\end{align}
Consider also the rate of change of $h$ as the interval is
expanded to the right, while keeping its left edge fixed:
\begin{align}
\frac{\partial h}{\partial L} &= \frac{\partial}{\partial L}
    \left[-Q(x_0, L) \log Q(x_0, L)\right] \\
    &= -\left[1 + \log Q(x_0, L)\right]\frac{\partial Q}{\partial L} \\
    &= -\left[1 + \log Q(x_0, L)\right]f(x_0 + L).
\end{align}

The entropy of the precisional question is built up from
$h$ terms. The extra entropy from moving from $x_0$ to
$x_0 + \delta$, for small $\delta$, is
\begin{align}
\delta H &= h(x_0 + \delta, L) - h(x_0 + \delta, L - 2\delta) \\
 &\approx \delta \frac{\partial h}{\partial x_0}
    - \left[\delta \frac{\partial h}{\partial x_0}
            -2\delta \frac{\partial h}{\partial L}\right] \\
 &= 2\delta \frac{\partial h}{\partial L} \\
 &= -2\delta\left[1 + \log Q(x_0, L)\right]f(x_0 + L)
\end{align}
Therefore
\begin{align}
\frac{dH}{dx_0} &= -2\left[1 + \log Q(x_0, L)\right]f(x_0 + L) \\
  &= -2\left[1 + \log \left(F(x_0 + L) - F(x_0)\right)\right]f(x_0 + L)
\end{align}
